\begin{thebibliography}{999999999999999999999999999}
  \bibitem[FC]{FC} G. Faltings, C.-L. Chai, \booktitle{Degeneration of abelian varieties}, Springer-Verlag, Berlin, 1990. 
  \bibitem[Kato]{Kato} K. Kato, \booktitle{Logarithmic structures of Fontaine-Illusie}, Proceedings of the First JAMI Conference, Johns Hoplins Univ. Press (1990), 191--224.
  \bibitem[RZ]{RZ} L. Ribes, P. Zalesskii, \booktitle{Profinite groups}, Springer-Verlag, 2000.
  \bibitem[FJ]{FJ} M. Fried, M. Jarden, \booktitle{Field arithmetic (Second edition)}, Ergebnisse der Mathematik und ihrer Grenzgebiete. 3. Folge. A Series of Modern Surveys in Mathematics \textbf{11}, Springer-Verlag, Berlin, 2005.
  \bibitem[SGA1]{SGA1} A. Grothendieck, \booktitle{Rev\^etements \'etales et groupe fondamental}, S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie 1960--1961 (SGA 1), Lecture Notes in Mathematics \textbf{224}, Springer-Verlag, Berlin-New York, 1971.

  \bibitem[AbsTopIII]{AbsTopIII} 
  \bibitem[Indecomp]{Indecomp} A. Minamide, \booktitle{Indecomposability of various profinite groups arising from hyperbolic curves}, Okayama Math. J. \textbf{60} (2018), 175--208.
  \bibitem[IntIndecomp]{IntIndecomp} A. Minamide, S. Tsujimura, \booktitle{Internal indecomposability of profinite groups}, Adv. Math. \textbf{409} (2022), 108689.
  \bibitem[GroupPropDVF]{GroupPropDVF} A. Minamide, S. Tsujimura, 
  \bibitem[GroupPropHensel]{GroupPropHensel} A. Minamide, S. Tsujimura,
  \bibitem[GeneralAnabGroupProp]{GeneralAnabGroupProp} A. Minamide, S. Tsujimura, 
\end{thebibliography}
